A publishing infrastructure for AI-assisted academic authoring

### 2024-01-02 latex/manuscript.tex
latex: fix spelling in disclosure statements

The manuscripts' text used for evaluation in this article are available in their GitHub repositories, at \url{https://github.com/greenelab/ccc-manuscript}, \url{https://github.com/greenelab/phenoplier_manuscript} and \url{https://github.com/greenelab/manubot-gpt-manuscript}.
The source code of the Manubot AI Editor is available in GitHub, at \url{https://github.com/manubot/manubot-ai-editor}.

>>>>

The manuscripts' text used for evaluation in this article are available on their GitHub repositories, at \url{https://github.com/greenelab/ccc-manuscript}, \url{https://github.com/greenelab/phenoplier_manuscript} and \url{https://github.com/greenelab/manubot-gpt-manuscript}.
The source code of the Manubot AI Editor is available on GitHub, at \url{https://github.com/manubot/manubot-ai-editor}.
